Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Styling: removed unnecessary new lines

plot(outcome_count_plot)

@@

#Print the table
knitr::kable(parametrization_and_validation_count)

@@

#Print the table
knitr::kable(sensitivity_analysis_count)

@@

#Print the results
knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')

```
# Code availability

@@

#Print the results
knitr::kable(code_availability_count, caption = 'Code availability')

# Number of studies per disease 
## By outbreak type

@@

#Print table of results
knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
             col.names = c('Continent',
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Number/percent of studies by continent'
             )

>>>>

plot(outcome_count_plot)
```

@@

#Print the table
knitr::kable(parametrization_and_validation_count)
```

@@

#Print the table
knitr::kable(sensitivity_analysis_count)
```

@@

#Print the results
knitr::kable(code_and_data_availability_count, caption = 'Data use and availability')
```
# Code availability

@@

#Print the results
knitr::kable(code_availability_count, caption = 'Code availability')
```

# Number of studies per disease

## By outbreak type

@@

#Print table of results
knitr::kable(continents_studied_by_count %>% arrange(desc(percentage)),
             col.names = c('Continent',
                           'Number of studies',
                           'Percentage'
                           ),
             caption = 'Number/percent of studies by continent'
             )
```
